%کلمات کلیدی انگلیسی
\latinkeywords{network management, network monitoring, SNMP protocol, network discovery}
%چکیده انگلیسی

\en-abstract{
    The increasing development of computer networks has made its management very important. In general, the management of a system will include monitoring components, analyzing information, and taking action to approach the goal of that system. In other words, management and especially computer network management is a permanent process including monitoring, processing, planning, and action. The purpose of this project was to develop a tool for monitoring computer networks. With the development of this system, management information including traffic information, configuration information, warnings, etc. is collected and displayed to the user. So with this feature, the user can plan and act through this information. This system receives monitoring information from components with SNMP protocol through a management interface and displays it in an understandable way for the network manager. After receiving the management information in the system, it will be processed and finally stored in the databases. Also, the web user interface fetches this management information and displays it to the user. Another possibility that was added to this system to facilitate planning and action for management was network discovery. With this feature, the user can also get an overview of the network. At the end of the project, various functional and non-functional requirements of the system were examined and tested.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}